Age-related changes in plant growth and traits

### 2016-05-17 scripts/results_accessory_shorter.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3))
mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logx(mod)

mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
words.bottom.right.logx(mod)

mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
words.top.right.logx(mod)

mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
words.top.right(mod)
mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
words.bottom.right.logxy(mod)

mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
words.top.right.logxy(mod)

mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
words.top.right(mod)
mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

@@

### Plotting accessory costs that go into making a single seed - ignoring aborted tissues
* Bigger seeds have bigger fixed costs of making that seed (1st plot)
* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot)
* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",cex=1.2)
mod <- lm(seedcosts~seed_size, SummarySpp)
words.bottom.right.logxy(mod)
text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")

plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
mod <- lm(costs_per_seed~seed_size, SummarySpp)
words.bottom.left.logy(mod)
```

* Here is the plot just of seed set by propagule investment (for all individuals), showing the effect is true within and across species
* This is the complement to the plot of accessory costs  
* Replotting the same data by age, shows that the pattern is not age-driven
* At most, there are most "old" plants with very low seedset 
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

*Comparing proportion energy to propagules vs accessory cost per seed
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

###Relationship between tissue allocation and reproductive investment
* these data also tell the story of seedset being an important "component" and being lower in bigger species
* Proption pre-pollination costs completely unrelated to reproductive investment
* However, proportional investment in propagules decreases with increasing reproductive investment, because the bigger species investment more overall in reproduction and less in propagules
* There is also no pattern with respect to proportional investment in packaging and dispersal (R^2=0, p-value=0.959) and a slight decrease in aborted post-pollination tissues with increasing reproductive investment (R^2=0.0661, p-value=0.0002)
```{r, echo=FALSE,message=FALSE, ,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(repro_inv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
plot((prop_prepollen_all)~repro_inv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp(species),xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
words.top.right.logx(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

###What happens against RA
* Overall RA is correlated with reproductive investment and age
* These plots only include individuals that have some reproductive investment
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(log(RA)~log((repro_inv)),data=subset(SummaryInd,RA>0))
plot(RA~(repro_inv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp(species),log="xy")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
* This is true for many individual species as well as across species
* RA and seed count are also correlated, but mainly that no low RA individuals have high seed counts
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",ylab="# of buds produced",xlab="")
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
words.bottom.right.logxy(mod)

@@

###Shifts across age
* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
* this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
* only LEES shows a significant decline with age, although most species have a segative slope  
* there is a similar pattern for Propagule investment (not shown)  
* Table shows results, by species, for seedset by proportional height  
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp(species))
words.top.right(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

##Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28}
par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp$prop_propagule_mean
se1 <- SummarySpp$prop_propagule_se
plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$propagule_per_seed_mean
se1 <- SummarySpp$propagule_per_seed_se
plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_prepollen_all_mean
se1 <- SummarySpp$prop_prepollen_all_se
plot(mean1~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prepollen_all_per_seed_mean
se1 <- SummarySpp$prepollen_all_per_seed_se
plot((.01+prepollen_all_per_seed_mean)~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_packaging_dispersal_mean
se1 <- SummarySpp$prop_packaging_dispersal_se
plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp$packaging_dispersal_per_seed_mean
se1 <- SummarySpp$packaging_dispersal_per_seed_se
plot((packaging_dispersal_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_postpollen_aborted_mean
se1 <- SummarySpp$prop_postpollen_aborted_se
plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp$postpollen_aborted_per_seed_mean
se1 <- SummarySpp$postpollen_aborted_per_seed_se
plot((postpollen_aborted_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)

>>>>

mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3))
mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logx(mod)

mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
words.bottom.right.logx(mod)

mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
words.top.right.logx(mod)

mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
words.top.right(mod)
mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
mod <- lm(log(seed_size)~(accessory_per_seed),SummarySpp[["mean"]])
plot(accessory_per_seed~seed_size,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(total_weight)~log(accessory_per_seed),SummarySpp[["mean"]])
plot(accessory_per_seed~total_weight,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
words.bottom.right.logxy(mod)

mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
plot((accessory_per_seed)~seedset,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
words.top.right.logxy(mod)

mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
plot(log(accessory_per_seed)~log(prepollen_all_per_seed),SummarySpp[["mean"]], log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
words.top.right(mod)
mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

@@

### Plotting accessory costs that go into making a single seed - ignoring aborted tissues
* Bigger seeds have bigger fixed costs of making that seed (1st plot)
* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot)
* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
plot(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",cex=1.2)
mod <- lm(seedcosts~seed_size, SummarySpp[["mean"]])
words.bottom.right.logxy(mod)
text(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")

plot(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
text(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")
mod <- lm(costs_per_seed~seed_size, SummarySpp[["mean"]])
words.bottom.left.logy(mod)
```

* Here is the plot just of seed set by propagule investment (for all individuals), showing the effect is true within and across species
* This is the complement to the plot of accessory costs  
* Replotting the same data by age, shows that the pattern is not age-driven
* At most, there are most "old" plants with very low seedset 
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

*Comparing proportion energy to propagules vs accessory cost per seed
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

###Relationship between tissue allocation and reproductive investment
* these data also tell the story of seedset being an important "component" and being lower in bigger species
* Proption pre-pollination costs completely unrelated to reproductive investment
* However, proportional investment in propagules decreases with increasing reproductive investment, because the bigger species investment more overall in reproduction and less in propagules
* There is also no pattern with respect to proportional investment in packaging and dispersal (R^2=0, p-value=0.959) and a slight decrease in aborted post-pollination tissues with increasing reproductive investment (R^2=0.0661, p-value=0.0002)
```{r, echo=FALSE,message=FALSE, ,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(repro_inv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
plot((prop_prepollen_all)~repro_inv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp(species),xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
words.top.right.logx(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

###What happens against RA
* Overall RA is correlated with reproductive investment and age
* These plots only include individuals that have some reproductive investment
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
mod <- lm(log(RA)~log((repro_inv)),data=subset(SummaryInd,RA>0))
plot(RA~(repro_inv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp(species),log="xy")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
* This is true for many individual species as well as across species
* RA and seed count are also correlated, but mainly that no low RA individuals have high seed counts
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",ylab="# of buds produced",xlab="")
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

@@

legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
words.bottom.right.logxy(mod)

@@

###Shifts across age
* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
* this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
* only LEES shows a significant decline with age, although most species have a segative slope  
* there is a similar pattern for Propagule investment (not shown)  
* Table shows results, by species, for seedset by proportional height  
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp(species))
words.top.right(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

##Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28}
par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp$prop_propagule
se1 <- SummarySpp$prop_propagule_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$propagule_per_seed
se1 <- SummarySpp$propagule_per_seed_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_prepollen_all
se1 <- SummarySpp$prop_prepollen_all_se
plot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp$prepollen_all_per_seed
se1 <- SummarySpp$prepollen_all_per_seed_se
plot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_packaging_dispersal
se1 <- SummarySpp$prop_packaging_dispersal_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp$packaging_dispersal_per_seed
se1 <- SummarySpp$packaging_dispersal_per_seed_se
plot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp$prop_postpollen_aborted
se1 <- SummarySpp$prop_postpollen_aborted_se
plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp$postpollen_aborted_per_seed
se1 <- SummarySpp$postpollen_aborted_per_seed_se
plot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)
